S2. Additional figures and table

### 2021-09-08 Manuscript/Manuscript_Results.Rmd
update table output
and other small things

---
title: "Results"
date: "`r lubridate::today()`"
output:
  github_document:
    html_preview: false
---

@@

including results between 2010 and 2020 (included). The automatic search tools were used for MEDLINE, WOS and IEEE, while a manual search and importation was necessary for EMBASE and SCOPUS. The search was repeated manually also for MEDLINE, since, as reported in the methods, the web interface may return different results from the API.

@@

`r knitr::kable(search_results, caption = "Table 1. Distribution of retrieved records by source and session. For each source it is reported the number of records, percentage over the session total (after removing duplicates)' and, number or records specific for a source as absolute value and as percentage over the source total. SAll session shows records after joining and deduplication of the Session1 and Session2 dataset.")`

@@

`r knitr::kable(annotation_results, caption = "Table 2. Results of the automatic classifaction and manual review rounds. For each iteration, the cumulative number of positives and negative records and their sum (Total labelled) and percentage over total are shown. Also, the number of changes after review and their description is reported. \"Unlab.\" indicates unlabelled records marked for review. For each Iteration, also the number of features used by the engine is reported. The first row reports the results of the initial manual labelling of records, which acted as input for the automatic classification in Iteration 1. In Session2, the engine uses the labels at the end of Session1 to classify the newly added records.")`

@@

### Hyperparameter selection and performance evaluation

@@

@@

`r knitr::kable(perf_table, caption = "Table 3. Estimated performance summary. For each session, the number of reviewed records and the percentage over the total provide an idea of the work saved against manually labelling all retrieved records. Using a simple logistic model to predict a positive match from the probabilities outputted by the engine, the predictive distribution of the cumulative number of positive matches was computed and used to estimate the sensitivity and the efficiency of the engine for each session. Finally the Bayesian R^2 of the logistic models is reported. [PrI] represents the 90% Predictive Interval.")`

```{r performance plot, cache = FALSE, fig.width=12, fig.height=5, fig.cap="Figure 1. 90% Predictive distribution of the cumulative number of positive matches estimated by the logistic Bayesian models applied to the engine output. The distribution is depicted by the shaded area. The distribution is cut at the level of the observed cumulative distribution of positive matches (red dots), since there cannot be false positive in the dataset and predicted value below this line are not possible."}

>>>>

---
title: "Results"
date: "`r lubridate::today()`"
output:
  pdf_document:
    includes:
      in_header: header.tex
  github_document: default
---

@@

subsetting results between 2010 and 2020 (included). The automatic search tools were used for MEDLINE, WOS and IEEE, while a manual search and importation was necessary for EMBASE and SCOPUS. The search was repeated manually also for MEDLINE, since, as reported in the methods, the web interface may return different results from the API.

@@

`r print_table(search_results, caption = "Table 1. Distribution of retrieved records by source and session. For each source it is reported the number of records, percentage over the session total (after removing duplicates)' and, number or records specific for a source as absolute value and as percentage over the source total. SAll session shows records after joining and deduplication of the Session1 and Session2 dataset.")`

@@

`r print_table(annotation_results, caption = "Table 2. Results of the automatic classifaction and manual review rounds. For each iteration, the cumulative number of positives and negative records and their sum (Total labelled) and percentage over total are shown. Also, the number of changes after review and their description is reported. \"Unlab.\" indicates unlabelled records marked for review. For each Iteration, also the number of features used by the engine is reported. The first row reports the results of the initial manual labelling of records, which acted as input for the automatic classification in Iteration 1. In Session2, the engine uses the labels at the end of Session1 to classify the newly added records.")`

@@

### Hyperparameter selection

@@

### Performance evaluation

@@

`r print_table(perf_table, caption = "Table 3. Estimated performance summary. The table reports for each session, the number of reviewed records and the percentage over the total. Also, the posterior expected number of positive records, *Sensitivity* and *Work saved over random* (WSoR) are reported, with their 90% PrI truncated to a number of positive matches equal to the observed one. Finally the median Bayesian R^2 [90% CrI] of the logistic models is reported. [PrI] represents the 90% Predictive Interval while [trunc. PrI] indicate the residual PrI truncated at the observed realization (see. methods).")`

```{r performance plot, cache = FALSE, fig.width=12, fig.height=5, fig.cap="Figure 2. Observed cumulative number of positive matches (red dots) sorted by simple query ordering. The [trunc. 90% PrI] of the cumulative positive matches estimated by the logistic Bayesian model is shown as shaded area delimited by the 95% quantile of the PrI and by the observed number of positive matches (light blue lines). The median of the PrI is represented by a darker blue line."}

### 2021-09-08 Manuscript/S2.Additional_outputs.Rmd
update table output
and other small things

---
title: "S2. Additional figures and table"
date: "`r lubridate::today()`"
output:
  github_document:
    html_preview: false
    toc: yes
---

@@

Figure 1 show the mixture of the predictive distribution of the probability of a positive match, grouped by labelling status. The posterior samples for each record were extracted and joined in a global distribution; on this distribution, density was computed on the logit scale and then logistic transformed for display on a \[[0 - 1]\] scale. The light violet ridges show the distribution of the still unlabelled records.\
For each iteration, the thresholds which define the lower and the upper range of 98% predictive interval (PrI) respectively for the positive and negative records are shown. The zone included between these two boundaries defines the uncertainty zone; records whose 98% PrI intersects this zone requires manual review.\
Notice how the positive and negative densities start overlapping starting with the second iteration of Session 2. Meanwhile the distribution of the records to be reviewed shrink and shift towards the negative side, as positive records get found and labeled.

@@

`r knitr::kable(var_importance_s1, caption = 'Table 1. Term importance at the end of Session 1')`

`r knitr::kable(var_importance_s2, caption = 'Table 2. Term importance at the end of Session 2')`

@@

`r knitr::kable(grid_out_params, caption = 'Table 3. Hyperparameter clusters and best cluster subsets. For each cluster, the defining rules and mean Sens. x Eff. is shown, followed by the per-cluster best set results.')`

>>>>

---
title: "S2. Additional figures and table"
date: "`r lubridate::today()`"
output:
  # pdf_document:
  #   toc: yes
  #   includes:
  #     in_header: header.tex
  github_document:
    toc: yes
---

@@

Figure 1 show the mixture of the predictive distribution of the probability of a positive match, grouped by labelling status. The posterior samples for each record were extracted and joined in a global distribution; on this distribution, density was computed on the logit scale and then logistic transformed for display on a $[0 - 1]$ scale. The light violet ridges show the distribution of the still unlabelled records.\
For each iteration, the thresholds which define the lower and the upper range of 98% predictive interval (PrI) respectively for the positive and negative records are shown. The zone included between these two boundaries defines the uncertainty zone; records whose 98% PrI intersects this zone requires manual review.\
Notice how the positive and negative densities start overlapping starting with the second iteration of Session 2. Meanwhile the distribution of the records to be reviewed shrink and shift towards the negative side, as positive records get found and labeled.

@@

`r print_table(var_importance_s1, caption = 'Table 1. Term importance at the end of Session 1.')`

`r print_table(var_importance_s2, caption = 'Table 2. Term importance at the end of Session 2.')`

@@

`r print_table(grid_out_params, caption = 'Table 3. Hyperparameter clusters and best cluster subsets. For each cluster, the defining rules and mean Sens. x Eff. is shown, followed by the per-cluster best set results.')`
